Pillar 1 - Sequential Pattern Mining

### 2019-02-11 Pillar 1 - Sequential Pattern Mining.Rmd
trivial change
re-organize sections

  # Identifying item
  mutate(
    item_G = paste(item, grade_ceil, sep = "_")
    )
```
## Additional General Dataframes for courses
#### Transcript with Preceding courses per student
```{r}
d_cumulative_transcript <-  d_transactions        %>%
  select(sequenceID, item, eventID)  %>%
  arrange(sequenceID, eventID, item) %>%
  group_by(sequenceID, eventID)      %>%
  summarize_all(paste, collapse=" ") %>%
  arrange(sequenceID, eventID)       %>%
  mutate(
    course_all  = paste(unique(d_transactions$item), collapse = " "),
    course_all  = str_split(course_all, pattern = " "),

@@

#### Courses that were taken before each course
```{r}
d_past_student_course <- d_cumulative_transcript %>%
  select(sequenceID, eventID, item, course_past) %>%
  unnest(item, .drop=F)

@@

sequences$taken <- make_sequence(item = item   )
sequences$PF    <- make_sequence(item = item_PF)
sequences$HL    <- make_sequence(item = item_HL)
#sequences_TPF  <- make_sequence(data = d_transactions_TPF, item = item_TPF) # compute ad hoc
sequences$G     <- make_sequence(data = d_transactions$G    , item = item_G  )

@@

# Remove objects
rm(
  my_apriori, clean_AR, compute_metrics, edit_AR, make_AR,
  AR
  )
```

## Sequence Rules
##TODO: fine tune parameters of cspade and ruleInduction, not taken --> fail

>>>>

  # Identifying item
  mutate(
    item_G = paste(item, grade_ceil, sep = "_")
    )
```

### Transcript with Preceding courses per student
```{r}
d_cumulative_transcript <-  d_transactions        %>%
  select(sequenceID, item, eventID)  %>%
  arrange(sequenceID, eventID, item) %>%
  group_by(sequenceID, eventID)      %>%
  summarize_all(paste, collapse=" ") %>%
  arrange(sequenceID, eventID)       %>%
  mutate(
    course_all  = paste(unique(d_transactions$item), collapse = " "),
    course_all  = str_split(course_all, pattern = " "),

@@

### Courses that were taken before each course
```{r}
d_past_student_course <- d_cumulative_transcript %>%
  select(sequenceID, eventID, item, course_past) %>%
  unnest(item, .drop=F)

@@

sequences$taken <- make_sequence(item = item   )
sequences$PF    <- make_sequence(item = item_PF)
sequences$HL    <- make_sequence(item = item_HL)
#sequences_TPF  <- make_sequence(data = d_transactions$TPF, item = item_TPF) # compute ad hoc
sequences$G     <- make_sequence(data = d_transactions$G    , item = item_G  )

@@

# Remove objects
rm(
  my_apriori, clean_AR, compute_metrics, edit_AR, make_AR,
  AR, transaction
  )
```

## Sequence Rules

###TODO: fine tune parameters of cspade and ruleInduction, not taken --> fail
